Paper figures

### 2020-03-22 voltagebudget/analysis/paper_figures_lossy.Rmd
Misc tweaks for lossy Figus

# HERE - need to run sims to make the osc_times df
osc_times <- NULL
p3 <- osc_times %>% 
  ggplot(aes(x=ts*1e3, y=ns, color=As)) +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  facet_grid(.~As) +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  ggtitle("Compression\nby oscillation")

@@

vb_norm_results %>% 
  filter(freq == 8) %>% 
  ggplot(aes(x=variances_pop, errors_pop, group=freq, color=state)) +
  geom_point(size=1.2, alpha=1) +
  geom_hline(yintercept = 0.5, alpha=1, color="grey", linetype="dashed") +
  annotate("text", x = 1, y = 0.54, label = expression(paste("E"[50]))) +
  labs(y="Normalized\nError", x="Normalized\ncompression") +
  ggtitle("A prediction for\npathological oscillation") +
  scale_color_manual("State", values=c("palevioletred3", "peachpuff3")) +
  theme_classic() +
  theme(legend.background = element_rect(colour ="black"),
        legend.position = "right") -> p3

(p1 | p2) / p3 +
  plot_layout(heights = c(1, 3)) + 
  plot_layout(guides = 'collect') +
  plot_annotation(tag_levels = 'a', tag_suffix = ".") 
ggsave("figures/lossy_fig10.png", dpi=600)
```

>>>>

# HERE - need to run sims to make the osc_times df
osc_times <- NULL
p3 <- osc_times %>% 
  ggplot(aes(x=ts*1e3, y=ns, color=As)) +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  scale_color_continuous("Peak\namplitude (namps)", low="darkred", high="lightgoldenrod3") +
  facet_grid(.~As) +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  ggtitle("Compression\nby oscillation")
p3 <- plot_spacer()

@@

vb_norm_results %>% 
  filter(freq == 8) %>% 
  ggplot(aes(x=variances_pop, errors_pop, group=freq, color=state)) +
  geom_point(size=1.2, alpha=1) +
  geom_hline(yintercept = 0.5, alpha=1, color="grey", linetype="dashed") +
  annotate("text", x = 1, y = 0.54, label = expression(paste("E"[50]))) +
  labs(y="Normalized\nError", x="Normalized\ncompression") +
  ggtitle("The pathological\ncompression hypothesis") +
  scale_color_manual("State", values=c("palevioletred3", "peachpuff3")) +
  theme_classic() +
  theme(legend.background = element_rect(colour ="black"),
        legend.position = "right") -> p3

# Build figure
(p1 | p2) / p3 +
  plot_layout(heights = c(1, 3)) + 
  plot_layout(guides = 'collect') +
  plot_annotation(tag_levels = 'a', tag_suffix = ".") 
ggsave("figures/lossy_fig10.png", dpi=600)
```

# Figure 11 - VB intro
We don't have a reference, or there is no practical reference. Voltage budget analysis to the rescue!
```{r}
# HERE...
# Create VB intro
```

# Figure 12 - VB and E50
```{r}
# HERE
```
